Meta-learning in movement prediction problem of aperiodic time-series data

### 2024-09-19 doc/paper/paper.tex
Fixed untracked files

In summary, our main contributions include the following: First, we present a novel \textbf{feature combination technique} that extracts and combines features using both \verb|LSTM| and \verb|CNN| models. Second, we uncover hidden long-term dependencies, demonstrating experimentally that aperiodic time-series data not only rely on external factors but also exhibit dependencies with past period, which we call \textbf{hidden long-term dependencies}. Third, we introduce an efficient model parameter aggregation approach by employing ML algorithm in place of traditional ensemble models for combining parameters from multiple machine learning models. Finally, we validate our method through experiments on exchange rate datasets and show its effectiveness in comparison to the SOTA model, \verb|NHITS|.

>>>>

In summary, our main contributions include the following: First, we present a novel \textbf{feature combination technique} that extracts and combines features using both \verb|LSTM| and \verb|CNN| models. Second, we uncover hidden long-term dependencies, demonstrating experimentally that aperiodic time-series data not only rely on external factors but also exhibit dependencies with past period, which we call \textbf{hidden long-term dependencies}. Third, we introduce an \textbf{efficient model parameter aggregation approach} by employing ML algorithm in place of traditional ensemble models for combining parameters from multiple machine learning models. Finally, we validate our method through experiments on exchange rate datasets and show its effectiveness in comparison to the SOTA model, \verb|NHITS|.
